Learning \strips\ action models from {\em state-invariants}

### 2019-02-06 doc/ijcai-19-deductivelearning/deductivelearning.tex
complete version for sections 1,2 and 3 ijcai19 paper on deductive learning

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{insertPre_{p,\xi}})=&\{\neg pre_{p}(\xi), \neg eff_{p}(\xi),\\
&mode_{insert},\neg mode_{inval}\},\\
\cond(\mathsf{insertPre_{p,\xi}})=&\{\emptyset\}\rhd\{pre_{p}(\xi)\},\\
&\{pre_{q}(\xi)\}\rhd\{mode_{inval}\}.
\end{align*}
\end{small}
The same procedure is applied for action $insertPre_{q,\xi}$ to ban this programming action iff $pre_{q}(\xi)$ precondition is already set. A similar procedure is also applied to $\mathsf{insertEff_{p,\xi}}$ and $\mathsf{insertEff_{q,\xi}}$ actions for banning two {\em negative effects} or (two {\em positive effects}) that are considered {\em domain mutex}.

@@

>>>>

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{insertPre_{p,\xi}})=&\{\neg pre_{p}(\xi), \neg eff_{p}(\xi),\\
&mode_{insert},\neg mode_{inval}\},\\
\cond(\mathsf{insertPre_{p,\xi}})=&\{\emptyset\}\rhd\{pre_{p}(\xi)\},\\
&\{pre_{q}(\xi)\}\rhd\{mode_{inval}\}.
\end{align*}
\end{small}
The same procedure is applied for action $insertPre_{q,\xi}$ to ban this programming action iff $pre_{q}(\xi)$ precondition is already set. A similar procedure is also applied to $\mathsf{insertEff_{p,\xi}}$ and $\mathsf{insertEff_{q,\xi}}$ actions for banning two {\em negative effects} or (two {\em positive effects}) that are considered {\em domain mutex}:

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{insertEff_{p,\xi}})=&\{\neg eff_{p}(\xi), mode_{insert},\neg mode_{inval}\},\\
\cond(\mathsf{insertEff_{p,\xi}})=&\{\emptyset\}\rhd\{eff_{p}(\xi),\\
&\{pre_{q}(\xi),eff_{q}(\xi),pre_{p}(\xi)\}\rhd\{mode_{inval}\},\\
&\{\neg pre_{q}(\xi),eff_{q}(\xi),\neg pre_{p}(\xi)\}\rhd\{mode_{inval}\}.
\end{align*}
\end{small}

@@

\section{Related work}
\label{sec:related}
